The necessity of hypermedia RDF and an approach to achieve it

### 2012-03-01 eswc-2012/workshop2.tex
cleaning spellcheck
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@142 43ef1190-90fd-4dd7-a769-d0121f02b80e

While links are highly abundant across the LOD cloud, this paper will
argue that key links are missing to make it possible to traverse the
resulting graph and to enable read-write operations. Moreover, we will
argue that this shortcoming is due to that the community does not
adequately take into account the constraint known as ``Hypermedia as
the Engine of Application State'' (commonly abbreviated HATEOAS) from
the REST architectural style, see
\cite{Fielding_2000_Architectural-Styles}~Chapter~5.

In a read-only situation, the HATEOAS constraint requires that the
application can navigate from one resources to another using the
hypermedia links in the present resource \emph{only}, it should not
require any out-of-band information to do so. Thus, a RESTful protocol
should not require prior knowledge of a URI structure, but one may
define the protocol in terms of URI structure as long as the same
information can be gleened from the resources. Nor does it require
that all resources can be reached from any other resource. As such,
the constraint is not very strict, one could argue that as long as
there are some links, the protocol satisfies the HATEOAS constraint.

Since RDF is built on URIs, many of which can be dereferenced to
obtain further links, it lends itself well to RESTful protocols, but
it is debateable whether a protocol can be said to be RESTful if the
links doesn't enable any useful interactions. Importantly, if there is
to be such a thing as a RESTful read-write Semantic Web protocol,
there must be something in the RDF itself that can be used by
practical applications to write data. Therefore, whether the HATEOAS
constraint is satisfied must be judged on the basis of the practical
applications the protocol enables.

@@

\item[CM] Support for indiciating the interface method for requests
  (e.g. HTTP GET, POST, PUT, DELETE methods).

>>>>

While links are abundant across the LOD cloud, this paper will
argue that key links are missing to make it possible to traverse the
resulting graph and to enable read-write operations. Moreover, we will
argue that this shortcoming is due to that the community does not
adequately take into account the constraint known as ``Hypermedia as
the Engine of Application State'' (commonly abbreviated HATEOAS) from
the REST architectural style, see
\cite{Fielding_2000_Architectural-Styles}~Chapter~5.

In a read-only situation, the HATEOAS constraint requires that the
application can navigate from one resources to another using the
hypermedia links in the present resource \emph{only}, it should not
require any out-of-band information to do so. Thus, a RESTful protocol
should not require prior knowledge of a URI structure, but one may
define the protocol in terms of URI structure as long as the same
information can be gleaned from the resources. Nor does it require
that all resources can be reached from any other resource. As such,
the constraint is not very strict, one could argue that as long as
there are some links, the protocol satisfies the HATEOAS constraint.

Since RDF is built on URIs, many of which can be dereferenced to
obtain further links, it lends itself well to RESTful protocols, but
it is debatable whether a protocol can be said to be RESTful if the
links doesn't enable any useful interactions. Importantly, if there is
to be such a thing as a RESTful read-write Semantic Web protocol,
there must be something in the RDF itself that can be used by
practical applications to write data. Therefore, whether the HATEOAS
constraint is satisfied must be judged on the basis of the practical
applications the protocol enables.

@@

\item[CM] Support for indicating the interface method for requests
  (e.g. HTTP GET, POST, PUT, DELETE methods).
